---
title: "Report Data and Figures"
output: html_notebook
---

```{r libraries}
library(tidyverse)
library(writexl)
source("../shiny/mappingmuseums/src/calculate_outcomes.R")
source("../shiny/mappingmuseums/src/calculate_closure_lengths.R")

core_actor_types_with_children <- c(
  "armed forces",
  "civic organisation",
  "company",
  "education/research",
  "heritage",
  "leisure",
  "library/archive",
  "other organisation",
  "service",
  "society",
  "storage",
  "temporary museum",
  "trader",
  "transport provider"
)

museum_attribute_ordering <- c(
  "all",
  # size
  "unknown size",
  "small",
  "medium",
  "large",
  "huge",
  # governance
  "unknown governance",
  "private",
  "independent",
  "Historic Environment Scotland",
  "National Trust for Scotland",
  "National Trust",
  "English Heritage",
  "not-for-profit",
  "university",
  "other government",
  "local authority",
  "national",
  # region/country
  "Isle of Man",
  "Channel Islands",
  "Northern Ireland",
  "Wales",
  "Scotland",
  "England",
  "North East",
  "North West",
  "Yorks & Humber",
  "East Midlands",
  "West Midlands",
  "East of England",
  "London",
  "South East",
  "South West",
  # accreditation
  "unaccredited",
  "accredited",
  # subject
  "other",
  "mixed: other",
  "mixed: encyclopaedic",
  "mixed: bygones",
  "mixed",
  "war & conflict: other",
  "war & conflict: regiment",
  "war & conflict: navy",
  "war & conflict: military",
  "war & conflict: event or site",
  "war & conflict: castles & forts",
  "war & conflict: bunker",
  "war & conflict: airforce",
  "war & conflict",
  "utilities: water & waste",
  "utilities: gas & electricity",
  "utilities",
  "transport: other",
  "transport: mixed",
  "transport: trains & railways",
  "transport: cars & motorbikes",
  "transport: canals",
  "transport: buses & trams",
  "transport: bicycles",
  "transport: aviation",
  "transport",
  "services: other",
  "services: rnli",
  "services: police",
  "services: fire",
  "services",
  "sea & seafaring: other",
  "sea & seafaring: mixed",
  "sea & seafaring: lighthouses",
  "sea & seafaring: fishing",
  "sea & seafaring: boats & ships",
  "sea & seafaring",
  "science & technology: other",
  "science & technology: computing & gaming",
  "science & technology",
  "rural industry: other",
  "rural industry: windmills",
  "rural industry: watermills",
  "rural industry: textiles",
  "rural industry: rural life",
  "rural industry: forges",
  "rural industry: farming",
  "rural industry",
  "personality: other",
  "personality: scientific",
  "personality: religious",
  "personality: political",
  "personality: music",
  "personality: literary",
  "personality: explorer",
  "personality: art",
  "personality",
  "natural world: other",
  "natural world: mixed",
  "natural world: zoology",
  "natural world: herbaria & gardening",
  "natural world: geology",
  "natural world: fossils",
  "natural world: dinosaurs",
  "natural world",
  "medicine & health: other",
  "medicine & health: professional association",
  "medicine & health: hospital",
  "medicine & health",
  "local histories",
  "leisure & sport: other",
  "leisure & sport: toys & models",
  "leisure & sport: rugby & football",
  "leisure & sport: film cinema & tv",
  "leisure & sport: fairgrounds & amusements",
  "leisure & sport: cricket",
  "leisure & sport",
  "industry & manufacture: other",
  "industry & manufacture: mixed",
  "industry & manufacture: textiles",
  "industry & manufacture: steam & engines",
  "industry & manufacture: print",
  "industry & manufacture: potteries",
  "industry & manufacture: mining & quarrying",
  "industry & manufacture: metals",
  "industry & manufacture: industrial life",
  "industry & manufacture: clocks & watches",
  "industry & manufacture",
  "food & drink",
  "communications: other",
  "communications: radio",
  "communications: post",
  "communications",
  "buildings: other",
  "buildings: shops",
  "buildings: school",
  "buildings: penal",
  "buildings: palace",
  "buildings: houses (small)",
  "buildings: houses (medium)",
  "buildings: houses (large)",
  "buildings: civic",
  "buildings",
  "belief & identity: other",
  "belief & identity: religious buildings",
  "belief & identity: religion",
  "belief & identity: freemasons",
  "belief & identity: ethnic group",
  "belief & identity: church treasuries",
  "belief & identity",
  "arts: other",
  "arts: photography",
  "arts: music",
  "arts: literature",
  "arts: glass",
  "arts: fine & decorative arts",
  "arts: design",
  "arts: crafts",
  "arts: costume & textiles",
  "arts: ceramics",
  "arts",
  "archaeology: other",
  "archaeology: mixed",
  "archaeology: roman",
  "archaeology: prehistory",
  "archaeology: medieval",
  "archaeology: greek & egyptian",
  "archaeology",
  # destination outcome
  "mostly no move",
  "mostly within the same LAD",
  "mostly within the same region",
  "mostly within the UK",
  "mostly abroad",
  "mixed destinations",
  # collection share
  "'few'",
  "'some'",
  "'half'",
  "'most'",
  "'all'",
  # recipient count outcome
  "many",
  "> 5",
  "5",
  "4",
  "3",
  "2",
  "1",
  "0",
  # recipient outcome
  "mostly N/A",
  "mostly storage",
  "mostly museum service",
  "mostly museum",
  "mostly library/archive",
  "mostly temporary museum",
  "mostly heritage",
  "mostly education/research",
  "mostly society",
  "mostly civic organisation",
  "mostly service",
  "mostly armed forces",
  "mostly leisure",
  "mostly transport provider",
  "mostly other organisation",
  "mostly company",
  "mostly trader",
  "mostly individual",
  "mostly unspecified actor",
  "mostly end of existence",
  # event outcome
  "mostly kept",
  "mostly left-in-situ",
  "mostly rescued",
  "mostly recorded",
  "mostly modified",
  "mostly used",
  "mostly displayed",
  "mostly stored",
  "mostly loaned",
  "mostly moved",
  "mostly returned",
  "mostly transferred",
  "mostly sold",
  "mostly lost/stolen",
  "mostly damaged/destroyed",
  "mostly unknown",
  # reason for closure
  "financial",
  "low visitor numbers",
  "loss of premises",
  "destruction",
  "collections",
  "building",
  "strategic closure",
  "restructure of host organisation",
  "dispute",
  "life events",
  "staff"
)

purple = "#E4A8F0"
white = "#FFFFFF"
heatmap_fill_scale <- scale_fill_continuous(low=white, high=purple)

standard_bars_theme <- theme_minimal() +
  theme(
    plot.title = element_text(size=title_size),
    plot.subtitle = element_text(size=subtitle_size),
    legend.position = "Non",
    axis.title.x = element_text(size=axis_title_size),
    axis.title.y = element_text(size=axis_title_size),
    axis.text.x = element_text(size=axis_text_size),
    axis.text.y = element_text(size=axis_text_size)
  )

standard_heatmap_theme <- standard_bars_theme +
  theme(
    axis.text.x = element_text(angle=30, hjust=1)
  )

output_width <- 175
output_height <- 90
output_units <- "mm"
```

## data files
```{r data-files}
data_directory <- "../data/closure_data_01_08_2025"
museums_file <- paste(data_directory, "museums.csv", sep="/")
event_types_file <- paste(data_directory, "event_types.csv", sep="/")
super_events_file <- paste(data_directory, "super_events.csv", sep="/")
dispersal_events_file <- paste(data_directory, "dispersal_events.csv", sep="/")
```

## Load data
```{r}
event_types <- read_csv(event_types_file)
super_events <- read_csv(super_events_file)

dispersal_events <- read_csv(dispersal_events_file) |>
  mutate(
    event_stage_in_path = event_stage_in_path + 1,
    recipient_type = case_when(
      is.na(recipient_type) ~ "N/A",
      recipient_type %in% core_actor_types_with_children ~ paste("unspecified", recipient_core_type),
      recipient_type == "actor" ~ "unspecified actor",
      TRUE ~ recipient_type
    ),
    recipient_core_type = case_when(
      recipient_type == "N/A" ~ "N/A",
      recipient_type == "unspecified actor" ~ "unspecified actor",
      TRUE ~ recipient_core_type
    ),
    sender_type = case_when(
      is.na(sender_type) ~ "N/A",
      sender_type %in% core_actor_types_with_children ~ paste("unspecified", sender_core_type),
      sender_type == "actor" ~ "unspecified actor",
      TRUE ~ sender_type
    ),
    sender_core_type = case_when(
      is.na(sender_type) ~ "N/A",
      sender_type == "unspecified actor" ~ "unspecified actor",
      TRUE ~ sender_core_type
    ),
    recipient_region = case_when(
      recipient_type == "end of existence" ~ "end of existence",
      recipient_type == "N/A" ~ "N/A",
      !is.na(recipient_region) ~ recipient_region,
      !is.na(recipient_country) ~ recipient_country,
      !is.na(destination_region) ~ destination_region,
      !is.na(destination_country) ~ destination_country,
      TRUE ~ "unknown"
    ),
    sender_region = case_when(
      sender_type == "end of existence" ~ "end of existence",
      !is.na(sender_region) ~ sender_region,
      !is.na(sender_country) ~ sender_country,
      !is.na(sender_region) ~ sender_region,
      !is.na(sender_country) ~ sender_country,
      TRUE ~ "unknown"
    ),
    collection_status = case_when(
      collection_status == "collection" ~ "Objects from a museum collection",
      collection_status == "loan" ~ "Objects on loan to a museum",
      collection_status == "handling" ~ "Handling objects",
      collection_status == "museum-stuff" ~ "Other objects (e.g. display cases)"
    ),
    initial_museum_all = "all",
    sender_all = ifelse(!is.na(sender_size), "all", NA),
    recipient_all = ifelse(!is.na(recipient_size), "all", NA)
  )

senders <- dispersal_events |>
  select(
    actor_id=sender_id,
    name=sender_name,
    quantity=sender_quantity,
    sector=sender_sector,
    type=sender_type,
    size=sender_size,
    governance=sender_governance,
    accreditation=sender_accreditation,
    town=sender_town,
    county=sender_county,
    postcode=sender_postcode,
    region=sender_region,
    country=sender_country
  )
recipients <- dispersal_events |>
  select(
    actor_id=recipient_id,
    name=recipient_name,
    quantity=recipient_quantity,
    sector=recipient_sector,
    type=recipient_type,
    size=recipient_size,
    governance=recipient_governance,
    accreditation=recipient_accreditation,
    town=recipient_town,
    county=recipient_county,
    postcode=recipient_postcode,
    region=recipient_region,
    country=recipient_country
  )
actors <- rbind(senders, recipients) |>
  unique()

initial_museums <- dispersal_events |>
  select(
    museum_id=initial_museum_id,
    museum_name=initial_museum_name,
    size=initial_museum_size,
    governance=initial_museum_governance,
    governance_broad=initial_museum_governance_broad,
    subject_broad=initial_museum_subject_broad,
    subject=initial_museum_subject,
    region=initial_museum_region,
    country=initial_museum_country,
    accreditation=initial_museum_accreditation
  ) |>
  distinct() |>
  mutate(
    name=paste0(museum_name, " (", museum_id, ")")
  ) |>
  arrange(name)

collection_types <- dispersal_events |>
  mutate(
    collection_type = str_remove_all(collection_types, "\\[|\\]|'") |>
      str_split(",\\s*")
  ) |>
  unnest(collection_type) |>
  select(collection_type) |>
  unique() |>
  arrange(collection_type) |>
  filter(collection_type != "")

museums_including_crown_dependencies <- read_csv(museums_file) |>
  mutate(
    year_opened = ifelse(
      year_opened_1 == year_opened_2,
      year_opened_1,
      paste(year_opened_1, year_opened_2, sep=":")
    ),
    year_closed = case_when(
      year_closed_1 == 9999 ~ "N/A",
      year_closed_1 == year_closed_2 ~ as.character(year_closed_1),
      TRUE ~ paste(year_closed_1, year_closed_2, sep=":")
    ),
    all=factor(all, museum_attribute_ordering),
    size=factor(size, museum_attribute_ordering),
    governance=factor(governance, museum_attribute_ordering),
    governance_broad=factor(governance_broad, museum_attribute_ordering),
    subject=factor(subject, museum_attribute_ordering),
    subject_broad=factor(subject_broad, museum_attribute_ordering),
    accreditation=factor(accreditation, museum_attribute_ordering),
    region=factor(region, museum_attribute_ordering),
    country=factor(country, museum_attribute_ordering)
  )

closure_reasons <- super_events |>
  separate_rows(reason, sep = "; ") |>
  separate_wider_delim(
    reason,
    " - ",
    names=c("reason_core", "reason_core_or_child", "reason_specific"),
    too_few="align_start"
  ) |>
  mutate(
    reason_core_or_child=ifelse(
      is.na(reason_core_or_child),
      reason_core,
      paste(reason_core, "-", reason_core_or_child)
    ),
    reason_specific=ifelse(
      is.na(reason_specific),
      reason_core_or_child,
      paste(reason_core_or_child, "-", reason_specific)
    )
  ) |>
  left_join(museums_including_crown_dependencies, by="museum_id")

closure_outcomes <- get_outcomes_by_museum(super_events, dispersal_events)
closure_lengths <- get_closure_lengths_by_museum(
  super_events, dispersal_events, event_types, museums_including_crown_dependencies
)
closure_timeline_events <- get_closure_timeline_events(
  super_events, dispersal_events, event_types, museums_including_crown_dependencies
)

museums_including_crown_dependencies <- museums_including_crown_dependencies |>
  left_join(closure_outcomes, by="museum_id") |>
  left_join(
    closure_reasons |>
      select(museum_id, reasons_for_closure=super_reasons) |>
      unique(),
    by="museum_id"
  ) |>
  mutate(
    outcome_event_type=factor(outcome_event_type, museum_attribute_ordering),
    outcome_recipient_type=factor(outcome_recipient_type, museum_attribute_ordering),
    outcome_recipient_count=factor(outcome_recipient_count, museum_attribute_ordering),
    outcome_largest_share=factor(outcome_largest_share, museum_attribute_ordering),
    outcome_destination_type=factor(outcome_destination_type, museum_attribute_ordering)
  )
museums <- museums_including_crown_dependencies |>
  filter(!country %in% c("Channel Islands", "Isle of Man"))

```

## Helper functions

```{r}
closure_reasons_summary_table <- function(closure_reasons_table, reason_level) {
  number_of_closed_museums <- closure_reasons_table |>
    select(museum_id) |>
    distinct() |>
    nrow()
  closure_reasons_table |>
    group_by(.data[[reason_level]]) |>
    summarize(
      frequency=n_distinct(museum_id),
      percentage=round(frequency / number_of_closed_museums * 100, 1)
    ) |>
    ungroup()
}

closure_reasons_two_way_summary_table <- function(closure_reasons_table,
                                                  reason_level,
                                                  museum_grouping) {
  number_of_closed_museums <- closure_reasons_table |>
    select(museum_id) |>
    distinct() |>
    nrow()
  number_of_closed_museums_by_type <- closure_reasons_table |>
    select(museum_id, .data[[museum_grouping]]) |>
    distinct() |>
    group_by(.data[[museum_grouping]]) |>
    summarize(number_of_closures=n_distinct(museum_id))
  data_2_way <- closure_reasons_table |>
    filter(!is.na(reason_core)) |>
    group_by(.data[[museum_grouping]], .data[[reason_level]]) |>
    summarize(
      frequency=n_distinct(museum_id),
      percentage=round(frequency / number_of_closed_museums * 100, 1)
    ) |>
    ungroup() |>
    left_join(number_of_closed_museums_by_type, by=museum_grouping) |>
    group_by(.data[[museum_grouping]]) |>
    mutate(
      percentage_x=round(frequency / number_of_closures * 100, 1)
    ) |>
    ungroup() |>
    group_by(.data[[reason_level]]) |>
    mutate(
      percentage_y=round(frequency / sum(frequency) * 100, 1)
    ) |>
    ungroup() |>
    select(-number_of_closures)
  data_dimension_1_totals <- closure_reasons_table |>
    filter(!is.na(reason_core)) |>
    group_by(.data[[reason_level]]) |>
    summarize(
      !!sym(museum_grouping) := "all",
      frequency=n_distinct(museum_id),
      percentage=round(frequency / number_of_closed_museums * 100, 1),
      percentage_x=percentage,
      percentage_y=100
    ) |>
    ungroup()
  data_dimension_2_totals <- closure_reasons_table |>
    filter(!is.na(reason_core)) |>
    left_join(number_of_closed_museums_by_type, by=museum_grouping) |>
    group_by(.data[[museum_grouping]]) |>
    summarize(
      !!sym(reason_level) := "all",
      frequency=number_of_closures,
      percentage=round(frequency / number_of_closed_museums * 100, 1),
      percentage_x=100,
      percentage_y=percentage
    ) |>
    ungroup() |>
    distinct()
  data_all_totals <- closure_reasons_table |>
    filter(!is.na(reason_core)) |>
    summarize(
      !!sym(reason_level) := "all",
      !!sym(museum_grouping) := "all",
      frequency=number_of_closed_museums,
      percentage=100,
      percentage_x=100,
      percentage_y=100
    )
  data_2_way |>
    rbind(data_dimension_1_totals) |>
    rbind(data_dimension_2_totals) |>
    rbind(data_all_totals) |>
    mutate(
      !!sym(museum_grouping) := factor(.data[[museum_grouping]], museum_attribute_ordering)
    )
}

closure_outcomes_summary_table <- function(museums_table, outcome_type) {
  museums_table |>
    filter(!is.na(.data[[outcome_type]])) |>
    group_by(.data[[outcome_type]]) |>
    summarize(frequency=n()) |>
    ungroup() |>
    mutate(percentage=round(frequency / sum(frequency) * 100, 1))
}

closure_outcomes_two_way_summary_table <- function(museums_table,
                                                   outcome_type,
                                                   museum_grouping) {
  if (museum_grouping =="reason_core") {
    museums_table <- museums_table |>
      left_join(
        closure_reasons |>
          select(museum_id, reason_core),
        by="museum_id"
      )
  }
  closure_outcomes <- museums_table |>
    filter(!is.na(.data[[outcome_type]])) |>
    mutate(
      dimension_1=.data[[outcome_type]],
      dimension_2=.data[[museum_grouping]]
    )
  number_of_closed_museums <- closure_outcomes |>
    select(museum_id) |>
    distinct() |>
    nrow()
  number_of_closed_museums_dimension_1 <- closure_outcomes |>
    group_by(dimension_1) |>
    summarize(number_of_closures_dimension_1=n_distinct(museum_id)) |>
    ungroup()
  number_of_closed_museums_dimension_2 <- closure_outcomes |>
    group_by(dimension_2) |>
    summarize(number_of_closures_dimension_2=n_distinct(museum_id)) |>
    ungroup()
  data_2_way <- closure_outcomes |>
    group_by(dimension_1, dimension_2) |>
    summarize(
      frequency=n_distinct(museum_id),
      percentage=round(frequency / number_of_closed_museums * 100, 1)
    ) |>
    ungroup() |>
    left_join(number_of_closed_museums_dimension_1, by="dimension_1") |>
    left_join(number_of_closed_museums_dimension_2, by="dimension_2") |>
    group_by(dimension_1) |>
    mutate(
      percentage_y=round(frequency / number_of_closures_dimension_1 * 100, 1)
    ) |>
    ungroup() |>
    group_by(dimension_2) |>
    mutate(
      percentage_x=round(frequency / number_of_closures_dimension_2 * 100, 1)
    ) |>
    ungroup() |>
    select(-number_of_closures_dimension_1, -number_of_closures_dimension_2)
  data_dimension_1_totals <- closure_outcomes |>
    group_by(dimension_1) |>
    left_join(number_of_closed_museums_dimension_1, by="dimension_1") |>
    summarize(
      dimension_2="all",
      frequency=number_of_closures_dimension_1,
      percentage=round(frequency / number_of_closed_museums * 100, 1),
      percentage_x=percentage,
      percentage_y=100
    ) |>
    ungroup() |>
    distinct()
  data_dimension_2_totals <- closure_outcomes |>
    group_by(dimension_2) |>
    left_join(number_of_closed_museums_dimension_2, by="dimension_2") |>
    summarize(
      dimension_1="all",
      frequency=number_of_closures_dimension_2,
      percentage=round(frequency / number_of_closed_museums * 100, 1),
      percentage_x=100,
      percentage_y=percentage
    ) |>
    ungroup() |>
    distinct()
  data_all_totals <- closure_outcomes |>
    summarize(
      dimension_1="all",
      dimension_2="all",
      frequency=number_of_closed_museums,
      percentage=100,
      percentage_x=100,
      percentage_y=100
    )
  data_2_way |>
    rbind(data_dimension_1_totals) |>
    rbind(data_dimension_2_totals) |>
    rbind(data_all_totals)
}

closure_outcomes_over_time_table <- function(museums_table, outcome_type) {
  museums_table |>
    rowwise() |>
    mutate(
      year_closed = mean(c(year_closed_1, year_closed_2)),
      period_of_closure = ifelse(
        year_closed > 1999 & year_closed < 2005,
        "2000-2004",
        ifelse(
          year_closed < 2010,
          "2005-2009",
          ifelse(
            year_closed < 2015,
            "2010-2014",
            ifelse(
              year_closed < 2020,
              "2015-2019",
              "2020-2025"
            )
          )
        )
      ),
      period_of_closure = factor(
        period_of_closure, 
        levels = c("2000-2004", "2005-2009", "2010-2014", "2015-2019", "2020-2025"),
        ordered = TRUE
      )
    ) |>
    group_by(.data[[outcome_type]], period_of_closure) |>
    summarize(frequency=n()) |>
    ungroup() |>
    group_by(period_of_closure) |>
    mutate(percentage=round(frequency / sum(frequency) * 100, 1)) |>
    ungroup()
}

closure_outcomes_over_time_two_way_table <- function(
    museums_table, outcome_type, museum_grouping
) {
  museums_table |>
    rowwise() |>
    mutate(
      year_closed = mean(c(year_closed_1, year_closed_2)),
      period_of_closure = ifelse(
        year_closed > 1999 & year_closed < 2005,
        "2000-2004",
        ifelse(
          year_closed < 2010,
          "2005-2009",
          ifelse(
            year_closed < 2015,
            "2010-2014",
            ifelse(
              year_closed < 2020,
              "2015-2019",
              "2020-2025"
            )
          )
        )
      ),
      period_of_closure = factor(
        period_of_closure, 
        levels = c("2000-2004", "2005-2009", "2010-2014", "2015-2019", "2020-2025"),
        ordered = TRUE
      )
    ) |>
    group_by(.data[[museum_grouping]], .data[[outcome_type]], period_of_closure) |>
    summarize(frequency=n()) |>
    ungroup() |>
    group_by(period_of_closure) |>
    mutate(percentage=round(frequency / sum(frequency) * 100, 1)) |>
    ungroup()
}
```

## Tables
```{r tables}
reasons_for_closure <- closure_reasons_summary_table(
  closure_reasons, "reason_core"
)
reasons_vs_governance <- closure_reasons_two_way_summary_table(
  closure_reasons, "reason_core", "governance_broad"
) |>
  rename(governance=governance_broad)
reasons_vs_size <- closure_reasons_two_way_summary_table(
  closure_reasons, "reason_core", "size"
)
reasons_vs_subject <- closure_reasons_two_way_summary_table(
  closure_reasons, "reason_core", "subject_broad"
) |>
  rename(subject=subject_broad)

outcomes_events <- closure_outcomes_summary_table(
  museums_including_crown_dependencies, "outcome_event_type"
)
outcomes_recipients <- closure_outcomes_summary_table(
  museums_including_crown_dependencies, "outcome_recipient_type"
)
outcomes_recipient_counts <- closure_outcomes_summary_table(
  museums_including_crown_dependencies, "outcome_recipient_count"
)
outcomes_destinations <- closure_outcomes_summary_table(
  museums_including_crown_dependencies, "outcome_destination_type"
)
outcomes_events_vs_governance <- closure_outcomes_two_way_summary_table(
  museums_including_crown_dependencies, "outcome_event_type", "governance_broad"
) |>
  rename(outcome_event_type=dimension_1, governance=dimension_2)
outcomes_over_time <- closure_outcomes_over_time_table(
  museums_including_crown_dependencies |>
    filter(!is.na(outcome_event_type)),
  "outcome_event_type"
)
outcomes_over_time_vs_governance <- closure_outcomes_over_time_two_way_table(
  museums_including_crown_dependencies |>
    filter(!is.na(outcome_event_type)),
  "outcome_event_type",
  "governance_broad"
)

closure_lengths_summary <- closure_lengths |>
  group_by(closure_length_category) |>
  summarize(count=n()) |>
  ungroup()

write_xlsx(
  list(
    "Data Dictionary"=read_csv("dictionaries/data_dictionary_closures.csv"),
    "Reasons for Closure"=reasons_for_closure,
    "Reasons by Governance"=reasons_vs_governance |>
      select(-percentage_x, -percentage_y),
    "Reasons by Size"=reasons_vs_size |>
      select(-percentage_x, -percentage_y),
    "Reasons by Subject"=reasons_vs_subject |>
      select(-percentage_x, -percentage_y),
    "Collection Outcomes"=outcomes_events |>
      rename(collection_outcome=outcome_event_type),
    "Collection Recipients"=outcomes_recipients |>
      rename(collection_recipient_type=outcome_recipient_type),
    "Collection Recipient Counts"=outcomes_recipient_counts |>
      rename(collection_recipient_count=outcome_recipient_count),
    "Collection Destinations"=outcomes_destinations |>
      rename(collection_destination=outcome_destination_type),
    "Outcomes by Governance"=outcomes_events_vs_governance |>
      rename(collection_outcome=outcome_event_type) |>
      select(-percentage_x, -percentage_y),
    "Outcomes Over Time"=outcomes_over_time |>
      rename(collection_outcome=outcome_event_type),
    "Outcomes Over Time by Governance"=outcomes_over_time_vs_governance |>
      rename(collection_outcome=outcome_event_type),
    "Closure Lengths"=closure_lengths_summary
  ),
  "tables/closures_2000-2025.xlsx"
)
```

## Figures

### Figure 19
Reasons for closure, UK museums 2000-25
```{r reasons}
figure_19 <- ggplot(
  reasons_for_closure |>
    mutate(
      reason_core=ifelse(
        reason_core == "restructure of host organisation",
        "restructure of host org.",
        reason_core
      )
    ),
  aes(x=frequency, y=reorder(reason_core, frequency))
) +
  geom_col(fill=purple) +
  geom_text(aes(label=frequency), hjust="left", nudge_x=1, size=3) +
  labs(
    title="Reasons for Museum Closure, 2000-2025",
    y="Reason for closure",
    x="Number of closures where reason is cited"
  ) +
  standard_bars_theme
ggsave("figures/fig19.svg", figure_19, width=output_width, height=output_height, units=output_units, bg="white")
figure_19
```

### Figure 20
Outcomes for the collection after closure, UK museums 2000-25
```{r reasons}
figure_20 <- ggplot(
  outcomes_events,
  aes(x=frequency, y=reorder(outcome_event_type, frequency))
) +
  geom_col(fill=purple) +
  geom_text(aes(label=frequency), hjust="left", nudge_x=1, size=3) +
  labs(
    title="What happened to collections after closure, 2000-2025",
    y="Collection outcome",
    x="Number of museums"
  ) +
  standard_bars_theme
ggsave("figures/fig20.svg", figure_20, width=output_width, height=output_height, units=output_units, bg="white")
figure_20
```

### Figure 22
The number of recipients for collections from closed museums, 2000-25
```{r reasons}
figure_22 <- ggplot(
  outcomes_recipient_counts,
  aes(x=frequency, y=outcome_recipient_count)
) +
  geom_col(fill=purple) +
  geom_text(aes(label=frequency), hjust="left", nudge_x=1, size=3) +
  labs(
    title="How many recipients collections went to after closure, 2000-2025",
    y="Number of recipients",
    x="Number of museums"
  ) +
  standard_bars_theme
ggsave("figures/fig22.svg", figure_22, width=output_width, height=output_height, units=output_units, bg="white")
figure_22
```

### Figure 23
Destination of collections from closed museums, 2000-25
```{r reasons}
figure_23 <- ggplot(
  outcomes_destinations |>
    filter(outcome_destination_type != "mostly unknown") |>
    mutate(percentage=round(frequency / sum(frequency) * 100, 1)),
  aes(x=percentage, y=outcome_destination_type)
) +
  geom_col(fill=purple) +
  geom_text(aes(label=paste0(percentage, "%")), hjust="left", size=3) +
  scale_x_continuous(limits=c(0, 50)) +
  labs(
    title="Where did collections go after closure, 2000-2025",
    y="Destination",
    x="Percentage of closures"
  ) +
  standard_bars_theme
ggsave("figures/fig23.svg", figure_23, width=output_width, height=output_height, units=output_units, bg="white")
figure_23
```

### Figure 26
Outcomes for the collection after closure, UK museums 2000-25
```{r reasons}
figure_26 <- ggplot(
  outcomes_events_vs_governance |>
    filter(governance == "local authority", outcome_event_type != "all"),
  aes(x=percentage_x, y=reorder(outcome_event_type, percentage_x))
) +
  geom_col(fill=purple) +
  geom_text(aes(label=paste0(percentage_x, "%")), hjust="left", nudge_x=1, size=3) +
  scale_x_continuous(limits=c(0, 60)) +
  labs(
    title="What happened to collections after closure, 2000-2025",
    y="Collection outcome",
    x="Percentage of local authority museums"
  ) +
  standard_bars_theme
ggsave("figures/fig26.svg", figure_26, width=output_width, height=output_height, units=output_units, bg="white")
figure_26
```

### Figure 29
Outcomes for the collection after closure, UK museums 2000-25
```{r reasons}
figure_29 <- ggplot(
  outcomes_events_vs_governance |>
    filter(governance == "independent", outcome_event_type != "all"),
  aes(x=percentage_x, y=reorder(outcome_event_type, percentage_x))
) +
  geom_col(fill=purple) +
  geom_text(aes(label=paste0(percentage_x, "%")), hjust="left", nudge_x=1, size=3) +
  scale_x_continuous(limits=c(0, 40)) +
  labs(
    title="What happened to collections after closure, 2000-2025",
    y="Collection outcome",
    x="Percentage of independent museums"
  ) +
  standard_bars_theme
ggsave("figures/fig29.svg", figure_29, width=output_width, height=output_height, units=output_units, bg="white")
figure_29
```

### Figure 31
Outcomes for the collection after closure, UK museums 2000-25
```{r reasons}
figure_31 <- ggplot(
  outcomes_events_vs_governance |>
    filter(governance == "private", outcome_event_type != "all"),
  aes(x=percentage_x, y=reorder(outcome_event_type, percentage_x))
) +
  geom_col(fill=purple) +
  geom_text(aes(label=paste0(percentage_x, "%")), hjust="left", nudge_x=1, size=3) +
  scale_x_continuous(limits=c(0, 60)) +
  labs(
    title="What happened to collections after closure, 2000-2025",
    y="Collection outcome",
    x="Percentage of private museums"
  ) +
  standard_bars_theme
ggsave("figures/fig31.svg", figure_31, width=output_width, height=output_height, units=output_units, bg="white")
figure_31
```

### Figure 21
Outcomes of closure over time, UK museums 2000-2025
```{r outcomes-over-time}
important_outcomes <- c("mostly transferred", "mostly sold", "mostly stored", "mixed", "mostly unknown", "mostly left-in-situ", "mostly kept", "mostly returned")
figure_21 <- ggplot(
  outcomes_over_time |> filter(outcome_event_type %in% important_outcomes), 
  aes(x=period_of_closure, y=percentage, colour=outcome_event_type)
) +
  geom_line(alpha=0.7, aes(group=outcome_event_type)) +
  geom_point() +
  geom_text(
    data=outcomes_over_time |> filter(period_of_closure=="2010-2014", outcome_event_type %in% important_outcomes),
    position=position_jitter(width=0.5, height=0.5, seed=123),
    aes(label=outcome_event_type, colour=outcome_event_type),
    size=3
  ) +
  scale_colour_brewer(palette="Paired") +
  guides(
    colour="none"
  ) +
  labs(
    title="Changing Outcomes of Museum Closure Over Time",
    x="Year of Closure",
    y="Percentage of museum closures",
    colour="Outcome of closure"
  ) +
  theme_minimal()
ggsave("figures/fig21.svg", figure_21, width=output_width, height=output_height, units=output_units, bg="white")
figure_21
```

### Figure 27
Outcomes of closure over time, UK museums 2000-2025
```{r outcomes-over-time}
fig_27_data <- outcomes_over_time_vs_governance |>
  filter(governance_broad == "local authority") |>
  group_by(period_of_closure) |>
  mutate(percentage=round(frequency / sum(frequency) * 100, 1)) |>
  ungroup() |>
  filter(outcome_event_type %in% important_outcomes)
important_outcomes <- c("mostly transferred", "mostly sold", "mostly stored", "mixed", "mostly unknown", "mostly left-in-situ", "mostly kept", "mostly returned")
figure_27 <- ggplot(
  fig_27_data, 
  aes(x=period_of_closure, y=percentage, colour=outcome_event_type)
) +
  geom_line(alpha=0.7, aes(group=outcome_event_type)) +
  geom_point() +
  geom_text(
    data=fig_27_data |> filter(period_of_closure=="2010-2014"),
    position=position_jitter(width=0.5, height=0.5, seed=123),
    aes(label=outcome_event_type, colour=outcome_event_type),
    size=3
  ) +
  scale_colour_brewer(palette="Paired") +
  guides(
    colour="none"
  ) +
  labs(
    title="Changing outcomes of local authority museum closure over time",
    x="Year of Closure",
    y="Percentage of museum closures",
    colour="Outcome of closure"
  ) +
  theme_minimal()
ggsave("figures/fig27.svg", figure_27, width=output_width, height=output_height, units=output_units, bg="white")
figure_27
```

### Figure 34
```{r reason-vs-subject}
reasons_vs_subject_main <- reasons_vs_subject |>
  filter(reason_core != "all", subject != "all") |>
  mutate(z_percent=as.numeric(scale(percentage_x)))
all_subjects <- reasons_vs_subject |>
  filter(subject == "all", reason_core != "all") |>
  mutate(z_percent=as.numeric(scale(percentage_x)))
all_reasons <- reasons_vs_subject |>
  filter(reason_core == "all", subject != "all") |>
  mutate(z_percent=as.numeric(scale(percentage_x)))
all_reasons_subjects <- reasons_vs_subject |>
  filter(reason_core == "all", subject == "all") |>
  mutate(z_percent=NaN)
reasons_vs_subject_with_scale <- reasons_vs_subject_main |>
  rbind(all_subjects) |>
  rbind(all_reasons) |>
  rbind(all_reasons_subjects)
figure_34 <- ggplot(
  reasons_vs_subject_with_scale |>
    mutate(
      reason_core=ifelse(
        reason_core == "restructure of host organisation",
        "restructure of host org.",
        reason_core
      )
    ),
  aes(
    x=factor(
      subject,
      c(
        "all",
        "archaeology",
        "arts",
        "belief & identity",
        "buildings",
        "communications",
        "food & drink",
        "industry & manufacture",
        "leisure & sport",
        "local histories",
        "medicine & health",
        "natural world",
        "personality",
        "rural industry",
        "science & technology",
        "sea & seafaring",
        "services",
        "transport",
        "utilities",
        "war & conflict",
        "mixed",
        "other"
      )
    ),
    y=factor(
      reason_core,
      c(
        "all",
        "unknown",
        "other",
        "destruction",
        "dispute",
        "collections",
        "staff",
        "restructure of host org.",
        "low visitor numbers",
        "strategic closure",
        "building",
        "life events",
        "loss of premises",
        "financial"
      )
    ),
    fill=z_percent
  )
) +
  geom_tile() +
  geom_text(aes(label=percentage_x), size=2.5, colour="black") +
  geom_hline(aes(yintercept=1.5)) +
  geom_vline(aes(xintercept=1.5)) +
  heatmap_fill_scale +
  labs(
    title="Reasons for museum closure by subject matter",
    x="Subject matter",
    y="Reason for closure"
  ) +
  standard_heatmap_theme +
  theme(
    axis.text.x = element_text(size=11),
    axis.text.y = element_text(size=11)
  )
ggsave("figures/fig34.svg", figure_34, width=output_width, height=output_height, units=output_units, bg="white")
figure_34
```

### Figure 35
```{r reason-vs-size}
reasons_vs_size_main <- reasons_vs_size |>
  filter(reason_core != "all", size != "all") |>
  mutate(z_percent=as.numeric(scale(percentage_x)))
all_sizes <- reasons_vs_size |>
  filter(size == "all", reason_core != "all") |>
  mutate(z_percent=as.numeric(scale(percentage_x)))
all_reasons <- reasons_vs_size |>
  filter(reason_core == "all", size != "all") |>
  mutate(z_percent=as.numeric(scale(percentage_x)))
all_reasons_sizes <- reasons_vs_size |>
  filter(reason_core == "all", size == "all") |>
  mutate(z_percent=NaN)
reasons_vs_size_with_scale <- reasons_vs_size_main |>
  rbind(all_sizes) |>
  rbind(all_reasons) |>
  rbind(all_reasons_sizes)
figure_35 <- ggplot(
  reasons_vs_size_with_scale |>
    mutate(
      reason_core=ifelse(
        reason_core == "restructure of host organisation",
        "restructure of host org.",
        reason_core
      )
    ),
  aes(
    x=size,
    y=factor(
      reason_core,
      c(
        "all",
        "unknown",
        "other",
        "destruction",
        "dispute",
        "collections",
        "staff",
        "restructure of host org.",
        "low visitor numbers",
        "strategic closure",
        "building",
        "life events",
        "loss of premises",
        "financial"
      )
    ),
    fill=z_percent
  )
) +
  geom_tile() +
  geom_text(aes(label=percentage_x), size=2.5, colour="black") +
  geom_hline(aes(yintercept=1.5)) +
  geom_vline(aes(xintercept=1.5)) +
  heatmap_fill_scale +
  labs(
    title="Reasons for museum closure by size",
    x="Size",
    y="Reason for closure"
  ) +
  standard_heatmap_theme +
  theme(
    axis.text.x = element_text(size=11),
    axis.text.y = element_text(size=11)
  )
ggsave("figures/fig35.svg", figure_35, width=output_width, height=output_height, units=output_units, bg="white")
figure_35
```

### Figure 24
Time taken by closed museums to dispose of objects
```{r outcomes-over-time}
figure_24 <- ggplot(
  closure_lengths_summary |>
    mutate(all="all") |>
    filter(!closure_length_category %in% c("all", "unknown")),
  aes(
    x=closure_length_category,
    y=count,
    group=all
  )
) +
  geom_point() +
  geom_line() +
  labs(
    title = "Time taken by closed museums to dispose of objects",
    x = "Length of disposal period (years)",
    y = "Number of Museums"
  ) +
  standard_bars_theme +
  theme(
    axis.text.x = element_text(angle=30, hjust=1)
  )
ggsave("figures/fig24.svg", figure_24, width=output_width, height=output_height, units=output_units, bg="white")
figure_24
```
